Blockchain System

### 2020-10-21 papers/execution-model/model.tex
update after discussion

\begin{definition}%[Account]
An \emph{account} is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
\end{definition}

\begin{definition}%[Contract]
An \emph{contract} is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
$\CODE$ is the code of the contract. 
\end{definition}

@@

\begin{definition}%[Contractor]
  A \emph{contractor} manages a smart contract. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

\begin{definition}%[Operation]
  \emph{Operations} are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

@@

\end{definition}
 \begin{definition}%[State of a node]
   The \emph{state of a node} is a tuple
   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

@@

Each node has (nondeterministic) rules to propose an operation.

\begin{mathpar}
  \inferrule[Node-Transfer]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans
    [\ACCOUNTS, \OP:: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-Originate]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \CHECKID (\ID, \CONTRACTS) \\
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans 
    [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}

  \inferrule[Block-System]
  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE\| \BLOCKCHAIN'}}
\end{mathpar}

@@

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\\\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS, \CONTRACTS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans 
    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
  }{
    \Angle{[
      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\ORIG,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME') \\
    \TIME'-\TIME < 60
  }{
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \SystemTrans \\
    \langle
      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
      \\
      [\PENDING, \Angle{\OP, \TIME'} :: \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
    \rangle
  }
\end{mathpar}

% \begin{equation}{}
% \frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS,
% \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$
% from ${pkh}$ running } \\ 
% \text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED,
% \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow
% \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\ 
% \text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)],
%  [\PENDING, $<$ (originate contract ${id}$ } \\
% \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
% \text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
%  \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
% \end{equation}
~\\
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
}{
    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']
    %}
    \BlockTrans
    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
    % }
}
\end{mathpar}
% \begin{equation}{}
% \frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$
% (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running
% ${code}$ init ${s}$) $>$ } \\ 
% \text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
% $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$,
% False), \CONTRACTORS, \TIME']}}}  
% \end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
\\
\text{ $\wedge$ checkArg(\CONTRACTORS, $puh, s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}\\
\text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
\text{\CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

>>>>

\subsection{Local Node}
\label{sec:local-node}

\begin{definition}%[Account]
  An \emph{account} is a tuple $\langle
  %\ALS,
  \PAK, \PUK
  %, \PKH
  \rangle $, where
  % $\ALS$ is the alias of the account,
  $\PAK$ is its private key and $\PUK$ is its public key.
  % and $\PKH$ is its public key hash . 
\end{definition}

% \begin{definition}%[Contract]
%   An \emph{contract} is a tuple $\langle
%   % \ALS,
%   \PUH, \CODE \rangle $, where
%   % $\ALS$ is the alias of the contract, 
%   $\PUH$ is its public hash, and
%   $\CODE$ is the code of the contract. 
% \end{definition}

\begin{definition}%[Operation]
  \emph{Operations} are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

\begin{definition}%[State of a node]
  The \emph{state of a node} is a tuple
  $\NODE = [\ACCOUNTS, \OPERATIONS]$ where $\ACCOUNTS$ is a set of
  accounts and
  $\OPERATIONS$ a set of operations.
\end{definition}

\subsection{Global}
\label{sec:global}

@@

\begin{definition}%[Contractor]
  A \emph{contractor} manages a smart contract. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

@@

\end{definition}

@@

Each node has (nondeterministic) rules to propose an operation.
When an operation $\OP$ appears, we check that the account is local by
looking up its public key $\OP.\PUK$ in the local accounts $\ACCOUNTS$ and
consider it signed with the corresponding private key $\PAK$.

\begin{mathpar}
  \inferrule[Node-Op]
  { % \CHECKACC (\OP.\PUK, \ACCOUNTS)
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
    % \\
    % \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS]
    \NodeTrans
    [\ACCOUNTS, \OP:: \OPERATIONS]
  }

  % \inferrule[Node-Originate]
  % {\CHECKACC (\PUK, \ACCOUNTS) \\
  %   % \CHECKID (\ID, \CONTRACTS) \\
  %   \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
  % }{
  %   [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
  %   \NodeTrans 
  %   [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
  % }
  %
  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}

  \inferrule[Block-System]
  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
  { {\overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\overline\NODE\| \BLOCKCHAIN'}}
\end{mathpar}

@@

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\\\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'/\PUH}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME) 
  }{
    \Angle{[
      \ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME < 60
  }{
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \SystemTrans \\
    \langle
      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
      \\
      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} :: \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
    \rangle
  }
\end{mathpar}

% \begin{equation}{}
% \frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS,
% \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$
% from ${pkh}$ running } \\ 
% \text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED,
% \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow
% \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\ 
% \text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)],
%  [\PENDING, $<$ (originate contract ${id}$ } \\
% \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
% \text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
%  \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
% \end{equation}
~\\
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
}{
    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']
    %}
    \BlockTrans
    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
    % }
}
\end{mathpar}
% \begin{equation}{}
% \frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$
% (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running
% ${code}$ init ${s}$) $>$ } \\ 
% \text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
% $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$,
% False), \CONTRACTORS, \TIME']}}}  
% \end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
% ~\\
% Rule 1 [proposal]:

% \begin{equation}{}
% \frac{\text{checkAcc($pkh$, \ACCOUNTS)  }}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
% \text{fee ${m}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
% ~\\
~\\
Rule 2 [injected]:
\begin{mathpar}
  \inferrule[Block-Call]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKARG (\CONTRACTORS, \PUH, \STRING) \\
    \OP =  \TRANSFER[\STRING]\NTEZ\PUK{\PUH}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK,\PUH, \STRING,\NTEZ, \MTEZ, \TIME)
  }{
    \Angle{[\ACCOUNTS, \OP :: \OPERATIONS], 
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    }
    \SystemTrans \\
    \Angle{[\ACCOUNTS, \OPERATIONS],
      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(
      \MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]
    }
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPuh(\CONTRACTORS, $puh$)}
% \\
% \text{ $\wedge$ checkArg(\CONTRACTORS, $puh,
%   s$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer ${n}$ from
%     ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: \OPERATIONS,
%     \CONTRACTS], 
%     [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
%     $\rangle$}\\
% \text{$\rightarrow$  $\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
%  \text{generateOph($pkh, puh, s, n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), }\\
% \text{\CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of counter]:
